\documentclass{article}

\begin{document} 

Rohan Grover
San Francisco, CA, United States rohannng@gmail.com
Technical Skills
Likes: java python scala typescript hadoop apache-spark distributed-computing functional-programming sql agile aop spring git javascript css unix bash


Experience


Jan 2017 ->Current Vice President – BlackRock
java, python, scala, hadoop, apache-spark, typescript, angular, rxjs, ngrx, spring
I am working with the fixed income alpha generation technologies team and have previously worked with the portfolio management tools team building,
enhancing and supporting fixed income portfolio managers and researchers develop and deploy alpha generating ideas. Some of my work is below.
Designing, implementing and established SDLC and CI/CD processes for Big Data processing infrastructure for alpha generation ( Solr, Hadoop, Spark,
bash, monorepo, maven )
Enhanced alpha generation python framework with new data loader and signal implementations ( Python, NumPy, Pandas )
Designed and implemented a portfolio targets CRUD and monitoring app. ( Java, TypeScript, Angular, NgRx, RxJs )
Led team to successfully deliver multiple feature enhancements to the portfolio management tools and implement dynamic auto scaling of services
infrastructure ( Java, Zookeeper, Design Patterns )


Aug 2013 ->Dec 2016 Associate – BlackRock
java, python, javascript, perl, unix, sybase, weblogic, jboss7.x, java-ee, spring, hibernate, apache-zookeeper, guava, sharding
I was working with portfolio management tools team and the core client processing team, building, enhancing and maintaining multiple technology solutions
supporting fixed income portfolio managers and back-office business operations respectively. Some of the my tasks are listed below.
Participated in analysis, design and development of distributed fixed income portfolio management application. ( Apache Ignite, Zookeeper, HSQL,
Swing, Functional paradigm, Concurrent )
Analyzed, designed and ported legacy C\# file formatting libraries to python.
Enhancement a fund order pipeline system for key connectivity enabling quicker order placement for cash PMs
Participating in the design and development of a new client order management system. ( Java, SDLC, Agile, AOP frameworks, SQL, data modeling )
Modernizing legacy apps, Weblogic to JBoss migration, Consolidation of business processes and related applications. ( J2EE, Unix )
Enhancing and maintaining a message processing app ecosystem comprising of various service oriented modules spread across multiple technologies. (
Java, MQ, Perl and T-SQL on Sybase )
Built a client facing web app using YUI, JS, JSP, Java, Weblogic and Sybase.
Wrote multiple perl scripts for ad-hoc reports, data analysis and task automation.


Jan 2009 ->Aug 2013 Software Engineer – Financial Sciences
java, javascript, ajax, sql, html, perl, weblogic, sybase, oracle
I was working on the full suite of Financial Sciences' Treasury Management products, developing new applications for the suite and continuously enhancing the
internal development framework and toolkit which is used for building new applications. The following is a list of some of my work.
Designed and implemented a forex accounting engine. (Java, Caching)
Designed and implemented a parsing engine for cash management based on the BAI2 format.
Coordinated and participated in the technical design, development and deployment of a complete implementation of the Financial Sciences' Treasury
Management product suite.
Coordinated the project, mentored the development and led the product design of C\# based Microsoft Excel plugin for OLAP real time data analysis
product.
Designed and implemented an OLAP based real time data analysis system as a product. ( Pentaho's mondrian, SOAP, Java, JavaScript ).
Designed a messaging engine based on the FIX protocol. ( Java, Concurrency )
Designed and implemented a socket based interface for Bloomberg using their Fixed Income Auto Execution Protocol. ( Java ).
Integrated Apache poi with the toolkit for excel import/export support.
Integrated JEP ( Java Expression Parser ) with the toolkit to handle expression parsing.
Led the design and integration of Flash charts in to the toolkit ( ActionScript 3.0, JavaScript )
Led the integration of OWASP-ESAPI open source, web application security control library with the toolkit
Designed and implemented a high-volume data processing engine which parsed and processed external XML formatted data.( Java )
Optimized and enhanced cash processing engines with better exception handling and parallel execution using threads


Sep 2008 ->Dec 2008 Programmer Intern – Linguistic Data Consortium
python, pyqt, unix, beautifulsoup
Managed and developed python scripts used for scrapping, converting and analyzing linguistic data from weblogs, news groups and other user oriented
websites.
Designed and developed a UI using pyQt for management and execution of the scrapper scripts.
May 2008 ->Aug 2008 Software Development Intern – Financial Sciences
js, html, java, xsl, xml, ajax, autocomplete
Developed applications using internal web application framework based on a js,ajax,xsl,xml,java and sybase stack.
Implemented new features to enhance internal toolkit capabilities. Notable few implementations include, autocomplete for html text boxes,Optimized
exception handling in the java api and enhanced logging capabilities using log4j

Jun 2006 ->Jun 2007 Project Engineer – Wipro Technologies
sap, abap
Implemented enhancements and modifications for a SAP 4.7 R/3 system with an underlying Oracle database using ABAP, Object Oriented ABAP and
Java.
Customized forms, screens, for the SD, PM, FICO modules of SAP 4.7 R/3 system.


Education
2007 -> 2009 M.S. Computer and Information Science – University of Pennsylvania
machine-learning, software-engineering, python, ruby, matlab, sql, java, js
Implemented various Machine Learning algorithms in matlab.
Designed and developed a Google map based location social network, a la Google latitude, but before Google latitude came out.
Implemented a socket based distributed mail system.
2002 ->2006 Bachelor of Technology in Computer Science – Jawaharlal Nehru Technological University

Tools
Favorite Editor: IntelliJ, PyCharm

\end{document}