\cventry
    {BlackRock} % Organization
    {Software Engineer - Associate} % Job Title
    {San Francisco, United States} % Location
    {Aug. 2013 - Dec. 2016} % Date(s)
    {java, python, javascript, perl, unix, sybase, weblogic, jboss7.x, java-ee, spring, hibernate, apache-zookeeper, guava, sharding}% Skills
    {
        I was working with portfolio management tools team and the core client processing team, building, enhancing and maintaining multiple technology solutions
        supporting fixed income portfolio managers and back-office business operations respectively. Key technologies and work follow. \newline
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Participated in analysis, design and development of distributed fixed income portfolio management application. ( Apache Ignite, Zookeeper, HSQL,Swing, Functional paradigm, Concurrent )}
        \item { Analyzed, designed and ported legacy C\# file formatting libraries to python.}
        \item { Enhanced a fund order pipeline system for key connectivity enabling quicker order placement for cash PMs}
        \item { Participating in the design and development of a new client order management system. ( Java, SDLC, Agile, AOP frameworks, SQL, data modeling )}
        \item { Modernizing legacy apps, Weblogic to JBoss migration, Consolidation of business processes and related applications. ( J2EE, Unix )}
        \item { Enhancing and maintaining a message processing app ecosystem comprising of various service oriented modules spread across multiple technologies. (Java, MQ, Perl and T-SQL on Sybase )}
        \item { Built a client facing web app using YUI, JS, JSP, Java, Weblogic and Sybase.}
        \item { Wrote multiple perl scripts for ad-hoc reports, data analysis and task automation.}
    \end{cvitems}
    }