\cventry
    {BlackRock} % Organization
    {Tech Lead - Vice President} % Job title
    {San Francisco, United States} % Location
    {Jan. 2017 - Dec. 2020} % Date(s)
    { python, java, hadoop, spark, nlp, jupyter, scala, typescript, angular, rxjs, ngrx, spring, development-management} % Skills
    {
        On the Fixed Income AlphaGen Technologies team and earlier with the Portfolio Management Tools team building, enhancing and supporting fixed income portfolio managers and researchers develop and deploy alpha generating ideas.
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Managing, leading, designing, implementing and establishing SDLC and CI/CD processes for big data processing platform for alpha generation research. ( Python, Solr, Hadoop, Spark, Bash, Monorepo, Maven, SparkNLP, Java, Scala ) }
        \item { Designing and implementing python client API library for text analytics. ( Python,Solr, Jupyter, Zeppelin, Pyspark, NLP, Scala )}
        \item { Enhanced alpha generation python framework with new data loader and signal implementations. ( Python, NumPy, Pandas )}
        \item { Designed and implemented a portfolio targets CRUD and monitoring app. ( Java, TypeScript, Angular, NgRx, RxJs ) }
        \item { Led team to successfully deliver multiple feature enhancements to the portfolio management tools and implement dynamic auto scaling of services infrastructure. ( Java, Zookeeper, Design Patterns )}
    \end{cvitems}
    }





