\cventry
    {Software Engineer} % Job title
    {Financial Sciences} % Organization
    {Jersey City, United States} % Location
    {Jan. 2009 - Aug. 2013} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        I was working on the full suite of Financial Sciences' Treasury Management products, developing new applications for the suite and continuously enhancing the
        internal development framework and toolkit which is used for building new applications. The following is a list of some of my work.
        \item { java, javascript, ajax, sql, html, perl, weblogic, sybase, oracle }
        \item { Designed and implemented a forex accounting engine. (Java, Caching)}
        \item { Designed and implemented a parsing engine for cash management based on the BAI2 format.}
        \item { Coordinated and participated in the technical design, development and deployment of a complete implementation of the Financial Sciences' Treasury Management product suite.}
        \item { Coordinated the project, mentored the development and led the product design of C\# based Microsoft Excel plugin for OLAP real time data analysis product.}
        \item { Designed and implemented an OLAP based real time data analysis system as a product. ( Pentaho's mondrian, SOAP, Java, JavaScript ).}
        \item { Designed a messaging engine based on the FIX protocol. ( Java, Concurrency )}
        \item { Designed and implemented a socket based interface for Bloomberg using their Fixed Income Auto Execution Protocol. ( Java ).}
        \item { Integrated Apache poi with the toolkit for excel import/export support.}
        \item { Integrated JEP ( Java Expression Parser ) with the toolkit to handle expression parsing.}
        \item { Led the design and integration of Flash charts in to the toolkit ( ActionScript 3.0, JavaScript )}
        \item { Led the integration of OWASP-ESAPI open source, web application security control library with the toolkit}
        \item { Designed and implemented a high-volume data processing engine which parsed and processed external XML formatted data.( Java )}
        \item { Optimized and enhanced cash processing engines with better exception handling and parallel execution using threads }
    \end{cvitems}
    }